Performance for the masses: Experiments with A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2016-01-26 GECCO/volunteer-clouds-gecco16.tex
Minor comments and changes for @JJ although I guess it is already sent :P

Using the browser as a computing resource in volunteer computing presents several advantages, 
but it remains a challenge to harness the browser's capabilities and
to model the user's behavior so that those capabilities can be
leveraged optimally. In this paper we present the results of several
experiments with a volunteer computing framework called {\sf NodIO}
that is easily deployable in using free cloud resources. We use
different browser configurations to find out which one is 
able to get the user to lend more computing cycles and test different
problems to check the influence it has on said performance.
From these experiments we can already draw some conclusions, besides
the fact that volunteer computing can be a valuable computing
resource: the user has to be kept engaged in some way to be able to
use as many computing cycles as possible, the client has to be built
to use the computer capabilities fully, and there is some common model
to all sets of users, following a common statistical distribution. As
a pragmatic result, establishing trust with the user by open sourcing
not only the software, but also the data, is essential to have an user
base as wide as possible.

>>>>

Using the browser as a computing resource in volunteer computing presents several advantages, 
but it remains a challenge to harness the browser's capabilities and
to model the user's behavior so that those capabilities can be
leveraged optimally. In this paper, we present the results of several
experiments with a volunteer computing framework called {\sf NodIO}
that is easily deployable in using free cloud resources. We use 
%Pablo: "deployable in using free cloud resources" is correct?
different browser configurations to find out which one is 
able to get the user to lend more computing cycles and test different
problems to check the influence it has on said performance.
% Pablo: so the objective is "to determine which browser conf. is able
% to get more computing power from the users", it isn't? 
% (to keep this in mind the rest of the paper). What is a "browser configuration"?
% (explain it with a phrase in the abstract)
From these experiments we can already draw some conclusions, besides
the fact that volunteer computing can be a valuable computing
resource: the user has to be kept engaged in some way to be able to
use as many computing cycles as possible, the client has to be built
to use the computer capabilities fully, and there is some common model
to all sets of users, following a common statistical distribution. As
a pragmatic result, establishing trust with the user by open sourcing
not only the software, but also the data, is essential to have a user %Pablo: remember, is "yiuser" :P
base as wide as possible.
